Arrows for Parallel Computation

### 2018-01-07 paper/content/main.tex
oops
that text in Sec.3

	%
	%%include abstract.lhs
	%
	%\newpage
	%\pagebreak
	\input{motivation}
	\input{relwork}
	\begin{flushright}

	\end{flushright}\section{Background}
	\label{sec:background}
	As a introduction, we here give a short overview over Arrows and GpH, the |Par| Monad, and Eden, the three parallel Haskells which we base our DSL on.
	\input{arrows}
	\input{parallelHaskells}
	%\pagebreak
	%\pagebreak
	%\pagebreak
	\input{parrows}
	%\pagebreak
	\input{basicSkeletons}
	%\pagebreak
	\input{syntacticSugar}
	%\pagebreak
	\input{futures}
	%\pagebreak
	\input{mapSkeletons}
	%\pagebreak
	\input{topologySkeletons}
	%\pagebreak
	\input{benchmarks}
	%%\pagebreak
	\input{conclusion}
	%\pagebreak
        \bibliographystyle{jfp}
	\bibliography{references,main}
        \appendix
	\input{utilityFunctions}
\end{document}

>>>>

	%
	%%include abstract.lhs
	%
	%\newpage
	%\pagebreak
	\input{motivation}
	\input{relwork}
	%\begin{flushright}
	%
	%\end{flushright}
        \section{Background}
	\label{sec:background}
	This section gives a short overview of Arrows
        (Section~\ref{sec:arrows}) and of GpH, the |Par| Monad, and
        Eden, the three parallel Haskells which we base our DSL on
        (Section~\ref{sec:parallelHaskells}).
        \input{arrows}
        \input{parallelHaskells}
	%\pagebreak
	%\pagebreak
	%\pagebreak
	\input{parrows}
	%\pagebreak
	\input{basicSkeletons}
	%\pagebreak
	\input{syntacticSugar}
	%\pagebreak
	\input{futures}
	%\pagebreak
	\input{mapSkeletons}
	%\pagebreak
	\input{topologySkeletons}
	%\pagebreak
	\input{benchmarks}
	%%\pagebreak
	\input{conclusion}
	%\pagebreak
        \bibliographystyle{jfp}
	\bibliography{references,main}
        \appendix
	\input{utilityFunctions}
\end{document}
